\documentclass[10pt, letterpaper]{article}

% ========== PREAMBLE ==========
\usepackage[
    ignoreheadfoot,
    top=1 cm,
    bottom=1 cm,
    left=1 cm,
    right=1 cm,
    footskip=1.0 cm
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0cm}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\renewcommand\labelitemi{$\circ$}
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0.5 cm
    ]
}{
    \end{itemize}
}
\newenvironment{onecolentry}{
    \begin{adjustwidth}{0.2 cm}{0.2 cm}
}{
    \end{adjustwidth}
}
\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

% ========== DOCUMENT ==========
\begin{document}

% ----- HEADER -----
\begin{center}
    {\fontsize{20pt}{20pt}\selectfont \textbf{Rahul C}}\\
    \vspace{0.15cm}
    {\faMapMarker*~Bengaluru, India \quad|\quad
     \href{mailto:rahulcy7@gmail.com}{\faEnvelope[regular]~rahulcy7@gmail.com} \quad|\quad
     \faPhone*~+91-8791338118 \quad|\quad
     \href{https://linkedin.com/in/rhlc}{\faLinkedinIn~rhlc} \quad|\quad
     \href{https://github.com/rhlc}{\faGithub~rhlc}}
\end{center}

% ----- SKILLS -----
\section{Skills}
\begin{onecolentry}
\textbf{Frontend:} HTML, CSS, JavaScript (ES6+), TypeScript, React.js, Redux, Context API, Next.js, Sass/SCSS, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, Golang, GraphQL, REST APIs, SQL, MongoDB \\
\textbf{Testing:} Jest, Cypress, Mocha \\
\textbf{DevOps & Cloud:} Google Cloud Platform (Firestore, App Engine, Compute Engine, Cloud Run), AWS (S3, EC2, Lambda, CloudFront), Docker, GitHub Actions \\
\textbf{Blockchain:} Ethereum, Solidity, Web3.js, Polygon, MetaMask, Hardhat \\
\textbf{Tools & Others:} Git, GitHub, Jira, Stripe, Figma, Postman \\
\textbf{Soft Skills:} Team Leadership, Mentoring, Problem Solving, Collaboration, Time Management
\end{onecolentry}


% ----- EXPERIENCE -----
\section{Experience}

\begin{twocolentry}{\textit{Aug 2023 -- Aug 2025}}
    \textbf{SDE II} \\
    \textit{Coreyo (Logistics Tech) — Bengaluru, India}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item Coreyo was a logistics tech company that aggregates multiple logistics providers to provide a single platform for booking and managing shipments.
    \item Led the frontend team to improve overall productivity and code quality, while reviewing pull requests and mentoring junior developers
    \item Migrated APIs from Nest.js (JavaScript) to Golang, this improved performance by 10x while reducing server costs drastically.
    \item Significantly reduced turnaround time for bug fixes by increasing team ownership and taking several productivity measures. 
    \item Modernized frontend codebase with modern React practices, improving maintainability and performance.
    \item Redesigned user journeys for key features to reduce friction as well number of steps while booking orders. 
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{\textit{Apr 2022 -- Aug 2023}}
    \textbf{Full Stack Developer} \\
    \textit{\href{https://app.neonsundae.xyz/}{Neon Sundae} (Web3 Platform) — Remote}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item Neon Sundae is a decentralized platform for Web3 communities, designed to provide a transparent freelance marketplace.
    \item Built Solidity smart contracts for NFT minting and airdropping on a EVM blockchain (Polygon).
    \item Integrated ReactJS and MetaMask, learned how web3 wallets function.
    \item Managed Google Cloud infrastructure for scalability and CI/CD.
    \item Spoke at Web3 conferences, increasing community engagement.
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{\textit{Oct 2020 -- Mar 2022}}
    \textbf{Software Engineer} \\
    \textit{Blur Social — Remote}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item Blur Social was a social media platform that allows users to share and discover content.
    \item Implemented JSON based token authentication and Stripe payment integration with subscription based pricing model.
    \item Built social engagement features (likes, comments) to improve daily active users.
    \item App gained some traction with say 20 active users and around 90 registered users. 
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{\textit{Sep 2020 -- Apr 2022}}
    \textbf{Full Stack Developer} \\
    \textit{\href{https://outofbox.co}{Outofbox}  (IT Services) — Remote}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item Outofbox is a web development and design agency.
    \item Delivered several responsive landing pages with modern CSS layouts.
    \item Improved client satisfaction through proactive communication.
\end{highlights}
\end{onecolentry}

% ----- EDUCATION -----
\section{Education}
\begin{twocolentry}{\textit{2012 -- 2015}}
    \textbf{B.Tech in Computer Science} \\
    \textit{Graphic Era Hill University — Dehradun, India}
\end{twocolentry}

% ----- AWARDS -----
\section{Awards}
\begin{onecolentry}
\begin{highlights}
    \item Topped in International-level computer olympiad (Uttarakhand, 2006).
\end{highlights}
\end{onecolentry}

\end{document}
